---
title: "Bellabeat: Marketing Strategy for Smart Devices"
author: "MW Kamdar"
date: "July 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)
library(rmdformats)
library(tidyverse)
library(lubridate)

setwd("E:/Admin/Documents/Google Data Analyst Course/Case Study 2 BellaBeat/Clean_Data")
DailyActivityDF <- read.csv("DailyActivityDF.csv")
DailySleepDF <- read.csv("DailySleepDF.csv")
HourlyActivityDF <- read.csv("HourlyActivityDF.csv")
HourlySleepDF <- read.csv("HourlySleepDF.csv")
```

## Business Task

### **Step 1:**
Use data from fitness trackers to gain insights on user behaviour.
\
\

### **Step 2:**
Use insights to guide marketing strategy


## Our Data

- **Sample size:** 35 fitbit users
\
\

- **Duration:** 2 months (12/03/16 - 12/05/16)
\
\

- **Attributes:** activity (intensity, duration, distance), step count, sleep, weight


## Key Findings

**Daily user averages:**

- Step count: 7253
- Distance covered: 5.2 kilometers
- Time spent sedentary:  16 hours 27 minutes

Fitbit users are more active than the average person (~5000 steps) BUT are still mostly inactive!

## Key Findings cont.
 
 
```{r sleep_vs_activitytype, echo=FALSE, message=FALSE, warning=FALSE}
ActivityType <- DailyActivityDF %>% 
pivot_longer(cols = c("VeryActiveDistance","ModeratelyActiveDistance","LightlyActiveDistance"),
             names_to = "ActiveType", values_to = "Distance")

ggplot(ActivityType, aes(x=Distance, y=MinutesAsleep, color=ActiveType)) + 
  geom_point() + geom_smooth(color="black", method = "lm") + facet_wrap(~ActiveType) + 
  labs(x = "Distance", y = "Minutes asleep", 
       title = "Distance vs minutes asleep for different intensities", color = "Intensity of activity") +
  scale_color_discrete(labels = c("Lightly Active", "Moderately Active", "Very Active"))
```

Activity can help regulate sleep. **Moderate intensity** appears to have the best effect.

## Key Findings cont.

```{r sleep_vs_calories, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(ActivityType, aes(x=Distance, y=Calories, color=ActiveType)) + 
  geom_point() + geom_smooth(color="black", method = "lm") + facet_wrap(~ActiveType) + 
  labs(x = "Distance", y = "Calories burned", 
       title = "Distance vs calories burned for different intensities", 
       color = "Intensity of activity") +
  scale_color_discrete(labels = c("Lightly Active", "Moderately Active", "Very Active"))
```

Measuring calories burned can help regulate weight. **Quantity** of activity is far more important than **intensity**.


## Recommendations

Incorporate the following ideas:

- People with fitness trackers are more active than the average person.
- Moderate activity is beneficial for sleep regulation and quality.
- Meeting activity goals can help in weight loss or weight management.
- Devices can track progress, and ensure the above goals are being met.

